\documentclass[12pt, a4paper, onecolumn]{article}

\usepackage{color}

\linespread{1.05} % Line spreading in the whole document (GLOBAL command)

\begin{document}
	
	\noindent
	{\LARGE List of default environments:}
	\begin{enumerate}
		
		\item abstract
		\item array
		\item center
		\item description
		\item displaymath
		\item document
		\item enumerate
		\item equation
		\item figure
		\item flushleft
		\item flushright
		\item itemize
		\item letter
		\item math
		\item minipage
		\item quotation
		\item quote
		\item table
		\item tabular
		\item thebibliography
		\item titlepage
		\item verbatim
		\item verse
		
	\end{enumerate}
	
	\noindent
	{\LARGE Description of some mentioned default environments:}
	
	\begin{description}
		
		\item \textbf{\textcolor{red}{abstract}}: Insert a summary of paper in early page of a paper
		
		\item \textbf{\textcolor{red}{array}}: Use in math texts. For create matrices and vectors.
		
		\item \textbf{\textcolor{red}{center}}: Center any text that placed in this environment.
		
		\item \textbf{\textcolor{red}{description}}: It's like dictionary. It hold some items and each item has a short description.
		
		\item \textbf{\textcolor{red}{displaymath}}: For show mathematical equations.
		
		\item \textbf{\textcolor{red}{document}}: Default main environment that we start writing in it.
		
		\item \textbf{\textcolor{red}{enumerate}}: Use for numbering. Not always use digits, It could use roman characters or some shapes or another things to enumerate items.
		
		\item \textbf{\textcolor{red}{equation}}: For insert some math equations.
		
		\item \textbf{\textcolor{red}{figure}}: For insert and use some images or figures.
		
		\item \textbf{\textcolor{red}{flushleft}}: Place text to the left.
		
		\item \textbf{\textcolor{red}{flushright}}: Place text to the right.
		
		\item \textbf{\textcolor{red}{itemize}}: For enumeration but not like enumerate environment.
		
		\item \textbf{\textcolor{red}{letter}}: It could be hold and include letter text. Just use in letter class.
		
		\item \textbf{\textcolor{red}{math}}: math equations insertion. Also \$..\$ is it's short form.
		
		\item \textbf{\textcolor{red}{minipage}}: Some separated parts of a text that explain something that not related to the main context of the text. It's like math books that have some "math game" among the flow. Or like biography of a scientist who mentioned It's equation or work in the text.
		
		\item \textbf{\textcolor{red}{quotation}}: Quotation of someone in the text.
		
		\item \textbf{\textcolor{red}{quote}}: Like quotation environment.
		
		\item \textbf{\textcolor{red}{table}}: To create tables.
		
		\item \textbf{\textcolor{red}{tabular}}: mostly use for create tables.
		
		\item \textbf{\textcolor{red}{thebibliography}}: Bibliography and references.
		
		\item \textbf{\textcolor{red}{titlepage}}: 
		
		\item \textbf{\textcolor{red}{verbatim}}: A mono-space environment that \textbf{not process} \LaTeX instructions and command. For example we use for some algorithms texts. 
		
		\item \textbf{\textcolor{red}{verse}}: For poems. We have "oldpoem" in Xepersia package for Persian poems.
		
	\end{description}
			
\end{document}